---
title: "Untitled"
author: "miryala vaishnavi"
date: "2026-04-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# ============================================================
# Aligned Rank Transform ANOVA for 2×2 Mixed Design
# ============================================================

library(ARTool)
library(emmeans)
library(dplyr)
library(ggplot2)

# ============================================================
# SECTION 0: DATA LOADING
# ============================================================

base <- getwd()

# ---------------- SINGLE PHONE RT ----------------
path_sp  <- file.path(base, "data_brsm", "single", "phone")
files_sp <- sort(list.files(path_sp, pattern = "\\.csv$", full.names = TRUE))

single_phone_rt <- rep(NA_real_, length(files_sp))

for (i in seq_along(files_sp)) {
  df <- read.csv(files_sp[i])

  if (startsWith(basename(files_sp[i]), "6"))
    df <- df[df$PlayerID != "Player_2", ]

  df <- df[df$Completed == "true" &
             df$InitialResponseTime.ms. > 0, ]

  if (nrow(df) > 0)
    single_phone_rt[i] <- mean(df$InitialResponseTime.ms., na.rm = TRUE)
}

# ---------------- MULTI PHONE RT ----------------
path_mp  <- file.path(base, "data_brsm", "multiple", "phone")
files_mp <- sort(list.files(path_mp, pattern = "\\.csv$", full.names = TRUE))

multi_phone_rt <- rep(NA_real_, length(files_mp))

for (i in seq_along(files_mp)) {
  df <- read.csv(files_mp[i])

  df <- df[df$Completed == "true" &
             df$InitialResponseTime.ms. > 0 &
             df$Level %in% 1:10, ]

  if (nrow(df) > 0)
    multi_phone_rt[i] <- mean(df$InitialResponseTime.ms., na.rm = TRUE)
}

# ---------------- SINGLE LAB RT ----------------
path_sl  <- file.path(base, "data_brsm", "single", "lab")
files_sl <- sort(list.files(path_sl, pattern = "\\.csv$", full.names = TRUE))

single_lab_rt_ms <- rep(NA_real_, length(files_sl))

for (i in seq_along(files_sl)) {
  df <- read.csv(files_sl[i])

  rt <- df$mouse.time[!is.na(df$mouse.time)]
  rt <- suppressWarnings(as.numeric(gsub("\\[|\\]", "", rt)))
  rt <- rt[!is.na(rt)]

  if (length(rt) > 0)
    single_lab_rt_ms[i] <- mean(rt) * 1000
}

# ---------------- MULTI LAB RT ----------------
path_ml  <- file.path(base, "data_brsm", "multiple", "lab")
files_ml <- sort(list.files(path_ml, pattern = "\\.csv$", full.names = TRUE))

multi_lab_rt_ms <- rep(NA_real_, length(files_ml))

for (i in seq_along(files_ml)) {

  df <- read.csv(files_ml[i], stringsAsFactors = FALSE)

  vals <- c()

  for (entry in df$mouse.time[!is.na(df$mouse.time)]) {

    parts <- strsplit(
      gsub("\\]\\[", "]|||[", entry),
      "\\|\\|\\|"
    )[[1]]

    for (p in parts) {

      cl <- gsub("\\[|\\]", "", p)

      if (nchar(trimws(cl)) > 0) {

        parsed <- suppressWarnings(
          as.numeric(strsplit(cl, ",")[[1]])
        )

        parsed <- parsed[!is.na(parsed)]

        if (length(parsed) > 0)
          vals <- c(vals, tail(parsed, 1) / length(parsed))
      }
    }
  }

  if (length(vals) > 0)
    multi_lab_rt_ms[i] <- mean(vals) * 1000
}

# ---------------- SANITY CHECK ----------------
cat("=== DATA LOADING COMPLETE ===\n")

cat(sprintf(
  "Single Phone: n = %d (non-NA = %d)\n",
  length(single_phone_rt),
  sum(!is.na(single_phone_rt))
))

cat(sprintf(
  "Single Lab:   n = %d (non-NA = %d)\n",
  length(single_lab_rt_ms),
  sum(!is.na(single_lab_rt_ms))
))

cat(sprintf(
  "Multi  Phone: n = %d (non-NA = %d)\n",
  length(multi_phone_rt),
  sum(!is.na(multi_phone_rt))
))

cat(sprintf(
  "Multi  Lab:   n = %d (non-NA = %d)\n\n",
  length(multi_lab_rt_ms),
  sum(!is.na(multi_lab_rt_ms))
))

# ============================================================
# SECTION 1: BUILD LONG FORMAT DATA FRAME
# ============================================================

n_single_files <- max(
  length(single_phone_rt),
  length(single_lab_rt_ms)
)

if (length(single_phone_rt) < length(single_lab_rt_ms))
  single_phone_rt <- c(
    single_phone_rt,
    rep(NA, length(single_lab_rt_ms) - length(single_phone_rt))
  )

if (length(single_lab_rt_ms) < length(single_phone_rt))
  single_lab_rt_ms <- c(
    single_lab_rt_ms,
    rep(NA, length(single_phone_rt) - length(single_lab_rt_ms))
  )

single_complete <- which(
  !is.na(single_phone_rt) &
    !is.na(single_lab_rt_ms)
)

cat(sprintf(
  "Single: %d participants have complete (Game + Lab) data\n",
  length(single_complete)
))

single_long <- data.frame(
  Participant = rep(
    paste0("S", single_complete),
    each = 2
  ),
  TargetLoad = "Single",
  Modality = rep(
    c("Game", "Lab"),
    times = length(single_complete)
  ),
  RT_ms = c(
    rbind(
      single_phone_rt[single_complete],
      single_lab_rt_ms[single_complete]
    )
  ),
  stringsAsFactors = FALSE
)

multi_complete <- which(
  !is.na(multi_phone_rt) &
    !is.na(multi_lab_rt_ms)
)

cat(sprintf(
  "Multi:  %d participants have complete (Game + Lab) data\n\n",
  length(multi_complete)
))

multi_long <- data.frame(
  Participant = rep(
    paste0("M", multi_complete),
    each = 2
  ),
  TargetLoad = "Multiple",
  Modality = rep(
    c("Game", "Lab"),
    times = length(multi_complete)
  ),
  RT_ms = c(
    rbind(
      multi_phone_rt[multi_complete],
      multi_lab_rt_ms[multi_complete]
    )
  ),
  stringsAsFactors = FALSE
)

long_df <- bind_rows(single_long, multi_long)

long_df$TargetLoad <- factor(
  long_df$TargetLoad,
  levels = c("Single", "Multiple")
)

long_df$Modality <- factor(
  long_df$Modality,
  levels = c("Game", "Lab")
)

long_df$Participant <- factor(long_df$Participant)

cat("=== LONG FORMAT DATA STRUCTURE ===\n")

cat(sprintf(
  "Total rows    : %d\n",
  nrow(long_df)
))

cat(sprintf(
  "Participants  : %d\n",
  nlevels(long_df$Participant)
))

cat(sprintf(
  "Single group  : %d participants\n",
  length(single_complete)
))

cat(sprintf(
  "Multiple group: %d participants\n",
  length(multi_complete)
))

cat("\nFirst few rows:\n")
print(head(long_df, 8))

cat("\nCell means (ms):\n")

print(
  long_df %>%
    group_by(TargetLoad, Modality) %>%
    summarise(
      n = n(),
      M_RT = round(mean(RT_ms), 2),
      SD_RT = round(sd(RT_ms), 2),
      Med_RT = round(median(RT_ms), 2),
      .groups = "drop"
    )
)

# ============================================================
# SECTION 2: ART ANOVA
# ============================================================

art_model <- art(
  RT_ms ~ TargetLoad * Modality + (1 | Participant),
  data = long_df
)

cat("=== ART MODEL SUMMARY ===\n")
print(summary(art_model))

cat("\n=== ART ANOVA TABLE ===\n")

art_anova <- anova(art_model)
print(art_anova)

# ============================================================
# SECTION 3: EFFECT SIZES
# ============================================================

cat("\n=== EFFECT SIZES (Partial Eta Squared) ===\n")

compute_eta2 <- function(F_val, df_num, df_den) {
  round((F_val * df_num) /
          (F_val * df_num + df_den), 4)
}

grade_eta2 <- function(e) {
  ifelse(
    e >= 0.14, "Large",
    ifelse(e >= 0.06, "Medium", "Small")
  )
}

F_load     <- art_anova$F[1]
df_load    <- art_anova$Df[1]
dfres_load <- art_anova$Df.res[1]

F_mod      <- art_anova$F[2]
df_mod     <- art_anova$Df[2]
dfres_mod  <- art_anova$Df.res[2]

F_int      <- art_anova$F[3]
df_int     <- art_anova$Df[3]
dfres_int  <- art_anova$Df.res[3]

eta2_load <- compute_eta2(F_load, df_load, dfres_load)
eta2_mod  <- compute_eta2(F_mod, df_mod, dfres_mod)
eta2_int  <- compute_eta2(F_int, df_int, dfres_int)

effect_df <- data.frame(
  Effect = c(
    "Target Load (Between)",
    "Modality (Within)",
    "TargetLoad × Modality (Interaction)"
  ),
  F_value = round(
    c(F_load, F_mod, F_int), 3
  ),
  df_num = c(df_load, df_mod, df_int),
  df_den = c(dfres_load, dfres_mod, dfres_int),
  p_value = round(
    c(
      art_anova$`Pr(>F)`[1],
      art_anova$`Pr(>F)`[2],
      art_anova$`Pr(>F)`[3]
    ),
    5
  ),
  partial_eta2 = c(
    eta2_load,
    eta2_mod,
    eta2_int
  ),
  Size = grade_eta2(
    c(
      eta2_load,
      eta2_mod,
      eta2_int
    )
  )
)

print(effect_df, row.names = FALSE)

# ============================================================
# SECTION 4: POST-HOC TESTS
# ============================================================

cat("\n=======================================================\n")
cat("POST-HOC PAIRWISE COMPARISONS\n")
cat("=======================================================\n\n")

interaction_p <- art_anova$`Pr(>F)`[3]

if (interaction_p < 0.05) {

  cat("*** Interaction is SIGNIFICANT → running post-hoc tests ***\n\n")

  ph <- art.con(
    art_model,
    "TargetLoad:Modality",
    adjust = "bonferroni"
  )

  print(ph)

} else {

  cat(
    "Interaction NOT significant (p =",
    round(interaction_p, 4),
    ")\n"
  )

  cat("→ Interpret main effects only\n\n")
}

cat("\n--- Main Effect Post-Hoc: MODALITY (Game vs Lab) ---\n")

ph_modality <- art.con(
  art_model,
  "Modality",
  adjust = "bonferroni"
)

print(ph_modality)

cat("\n--- Main Effect Post-Hoc: TARGET LOAD (Single vs Multiple) ---\n")

ph_load <- art.con(
  art_model,
  "TargetLoad",
  adjust = "bonferroni"
)

print(ph_load)

# ============================================================
# SECTION 5: SIMPLE EFFECTS ANALYSIS
# ============================================================

cat("\n=======================================================\n")
cat("SIMPLE EFFECTS ANALYSIS\n")
cat("=======================================================\n\n")

single_data <- long_df[
  long_df$TargetLoad == "Single",
]

wt_single <- wilcox.test(
  RT_ms ~ Modality,
  data = single_data,
  paired = TRUE,
  exact = FALSE
)

multi_data <- long_df[
  long_df$TargetLoad == "Multiple",
]

wt_multi <- wilcox.test(
  RT_ms ~ Modality,
  data = multi_data,
  paired = TRUE,
  exact = FALSE
)

game_data <- long_df[
  long_df$Modality == "Game",
]

wt_game <- wilcox.test(
  RT_ms ~ TargetLoad,
  data = game_data,
  exact = FALSE
)

lab_data <- long_df[
  long_df$Modality == "Lab",
]

wt_lab <- wilcox.test(
  RT_ms ~ TargetLoad,
  data = lab_data,
  exact = FALSE
)

alpha_corrected <- 0.05 / 4

cat(sprintf(
  "Bonferroni-corrected α for simple effects = %.4f\n\n",
  alpha_corrected
))

simple_effects <- data.frame(
  Comparison = c(
    "Game vs Lab | Single Target",
    "Game vs Lab | Multiple Target",
    "Single vs Multi | Game",
    "Single vs Multi | Lab"
  ),
  Test = c(
    "Wilcoxon SR (paired)",
    "Wilcoxon SR (paired)",
    "Mann-Whitney U",
    "Mann-Whitney U"
  ),
  Statistic = c(
    wt_single$statistic,
    wt_multi$statistic,
    wt_game$statistic,
    wt_lab$statistic
  ),
  p_value = round(
    c(
      wt_single$p.value,
      wt_multi$p.value,
      wt_game$p.value,
      wt_lab$p.value
    ),
    5
  ),
  Significant_after_Bonferroni = c(
    wt_single$p.value < alpha_corrected,
    wt_multi$p.value < alpha_corrected,
    wt_game$p.value < alpha_corrected,
    wt_lab$p.value < alpha_corrected
  )
)

print(simple_effects, row.names = FALSE)

# ============================================================
# SECTION 6: DESCRIPTIVE STATISTICS
# ============================================================

cat("\n=======================================================\n")
cat("CELL DESCRIPTIVES (for reporting)\n")
cat("=======================================================\n")

cell_stats <- long_df %>%
  group_by(TargetLoad, Modality) %>%
  summarise(
    n = n(),
    Mean_RT = round(mean(RT_ms), 2),
    Median_RT = round(median(RT_ms), 2),
    SD_RT = round(sd(RT_ms), 2),
    .groups = "drop"
  )

print(cell_stats)

cat("\nGame-Lab Gaps (Mean):\n")

gaps <- cell_stats %>%
  tidyr::pivot_wider(
    names_from = Modality,
    values_from = c(Mean_RT, Median_RT)
  ) %>%
  mutate(
    Gap_Mean = round(
      Mean_RT_Game - Mean_RT_Lab,
      2
    ),
    Gap_Median = round(
      Median_RT_Game - Median_RT_Lab,
      2
    )
  ) %>%
  select(
    TargetLoad,
    Mean_RT_Game,
    Mean_RT_Lab,
    Gap_Mean,
    Median_RT_Game,
    Median_RT_Lab,
    Gap_Median
  )

print(gaps)

# ============================================================
# SECTION 7: INTERACTION PLOT
# ============================================================

cat("\n=== Generating interaction plot ===\n")

cell_means <- long_df %>%
  group_by(TargetLoad, Modality) %>%
  summarise(
    Mean_RT = mean(RT_ms),
    SE_RT = sd(RT_ms) / sqrt(n()),
    .groups = "drop"
  )

interaction_plot <- ggplot(
  cell_means,
  aes(
    x = Modality,
    y = Mean_RT,
    group = TargetLoad,
    color = TargetLoad,
    shape = TargetLoad
  )
) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 4) +
  geom_errorbar(
    aes(
      ymin = Mean_RT - SE_RT,
      ymax = Mean_RT + SE_RT
    ),
    width = 0.1,
    linewidth = 0.8
  ) +
  scale_color_manual(
    values = c(
      "Single" = "steelblue",
      "Multiple" = "darkgreen"
    )
  ) +
  labs(
    title = "Interaction Plot: Target Load × Modality",
    subtitle = "Error bars = ±1 SE | Non-parallel lines = interaction",
    x = "Modality",
    y = "Mean Reaction Time (ms)",
    color = "Target Load",
    shape = "Target Load"
  ) +
  theme_minimal() +
  theme(
    panel.border = element_rect(
      color = "black",
      fill = NA
    ),
    plot.title = element_text(
      face = "bold",
      size = 14
    ),
    plot.subtitle = element_text(
      size = 10,
      color = "gray40"
    ),
    legend.position = "top"
  )

print(interaction_plot)



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
