---
title: "Project"
author: "Harshika"
date: "2026-03-04"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(dplyr)
library(purrr)

base <- getwd()
print(base)
path <- file.path(base, "data_brsm", "single", "phone")

files <- sort(list.files(path = path,
                         pattern = "\\.csv$",
                         full.names = TRUE))

# print(files)


path1 <- file.path(getwd(), "data_brsm", "multiple", "phone")

multiple_files <- sort(list.files(path = path1,
                         pattern = "\\.csv$",
                         full.names = TRUE))

# print(multiple_files)

single_phone <- map_df(files, function(f) {
  read.csv(f, stringsAsFactors = FALSE)
}, .id = "Player")

single_phone <- single_phone %>%
  select(Player, PlayerID, Timestamp, GameMode, Level, FinalScore,
         Completed, SuccessRate... , HitRate..., FalseAlarms,
         InitialResponseTime.ms., AvgInterTargetTime.ms., HitPositions.x.y.)

# str(single_phone)
length(unique(single_phone$Player))
table(single_phone$GameMode)
table(single_phone$Player)
colnames(single_phone[7])
names(single_phone) <- make.names(names(single_phone))
names(single_phone)
 # print(single_phone)
library(dplyr)

table(single_phone$GameMode)

names(single_phone) <- make.names(names(single_phone))
#names(single_phone)

single_phone$SuccessRate... <- as.numeric(single_phone$SuccessRate...)
single_phone$HitRate... <- as.numeric(single_phone$HitRate...)


single_participant_stats <- single_phone %>%
  filter(Completed == "true", InitialResponseTime.ms. > 0) %>%
  group_by(Player) %>%
  summarise(
    Mean_RT = mean(InitialResponseTime.ms., na.rm = TRUE),
    Mean_SuccessRate = mean(SuccessRate..., na.rm = TRUE),
    Mean_HitRate = mean(HitRate..., na.rm = TRUE),
    Mean_FalseAlarms = mean(FalseAlarms, na.rm = TRUE)
  )

print(single_participant_stats$Mean_RT)

single_stats <- data.frame(
  Mean_RT = mean(single_participant_stats$Mean_RT),
  SD_RT = sd(single_participant_stats$Mean_RT),

  Mean_SuccessRate = mean(single_participant_stats$Mean_SuccessRate),
  SD_SuccessRate = sd(single_participant_stats$Mean_SuccessRate),

  Mean_HitRate = mean(single_participant_stats$Mean_HitRate),
  SD_HitRate = sd(single_participant_stats$Mean_HitRate),

  Mean_FalseAlarms = mean(single_participant_stats$Mean_FalseAlarms),
  SD_FalseAlarms = sd(single_participant_stats$Mean_FalseAlarms)
)

print(single_stats)


single_level_stats <- single_phone %>%
  filter(Completed == "true", InitialResponseTime.ms. > 0) %>%
  group_by(Player, Level) %>%
  summarise(
    RT = mean(InitialResponseTime.ms., na.rm = TRUE),
    SuccessRate = mean(SuccessRate..., na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(Level) %>%
  summarise(
    Mean_RT = mean(RT),
    SD_RT = sd(RT),
    Mean_SuccessRate = mean(SuccessRate)
  )

table(single_phone$HitRate...)


rt_level_stats <- single_phone %>%
  filter(Completed == "true") %>%
  group_by(Player, Level) %>%
  summarise(
    RT = mean(InitialResponseTime.ms., na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(Level) %>%
  summarise(
    Mean_RT = mean(RT)
  )

print(rt_level_stats)


```


```{r}
library(ggplot2)
my_theme <- theme_minimal() +
  theme(
    panel.border = element_rect(color = "black", fill = NA, linewidth = 1),
    axis.line = element_line(color = "black")
  )

ggplot(
  single_phone %>% filter(Completed == "true", InitialResponseTime.ms. > 0),
  aes(x = InitialResponseTime.ms.)
) +
  geom_histogram(binwidth = 500, fill = "steelblue", color = "black") +
  labs(
    title = "Reaction Time Distribution (Single Target - Phone)",
    x = "Reaction Time (ms)",
    y = "Frequency"
  ) +
  theme_minimal() +
  my_theme


ggplot(
  single_phone %>% filter(Completed == "true", InitialResponseTime.ms. > 0),
  aes(x = factor(Level), y = InitialResponseTime.ms.)
) +
  geom_boxplot(fill = "steelblue") +
  labs(
    title = "Reaction Time Across Levels (Single Target - Phone)",
    x = "Level",
    y = "Reaction Time (ms)"
  ) +
  theme_minimal() +
  my_theme

ggplot(single_level_stats, aes(x = factor(Level), y = Mean_SuccessRate)) +
  geom_bar(stat = "identity", fill = "darkgreen") +
  labs(
    title = "Average Success Rate by Level (Single Target - Phone)",
    x = "Level",
    y = "Success Rate (%)"
  ) +
  ylim(0,100) +
  theme_minimal() +
  my_theme

ggplot(single_level_stats, aes(x = Level, y = Mean_SuccessRate)) +
  geom_line(color = "darkgreen", size = 1) +
  geom_point(size = 3) +
  labs(
    title = "Success Rate Trend Across Levels (Single Target - Phone)",
    x = "Level",
    y = "Success Rate (%)"
  ) +
  ylim(90,100) +
  theme_minimal() +
  my_theme

ggplot(single_phone, aes(x = FalseAlarms)) +
  geom_histogram(binwidth = 1, fill = "orange", color = "black") +
  labs(
    title = "Distribution of False Alarms (Single Target - Phone)",
    x = "Number of False Alarms",
    y = "Frequency"
  ) +
  theme_minimal() + 
  my_theme

ggplot(rt_level_stats, aes(x = Level, y = Mean_RT)) +
  geom_line(color = "red") +
  geom_point(size = 2) +
  labs(
    title = "Average Reaction Time Trend Across Levels(Single Game)",
    x = "Level",
    y = "Mean Reaction Time (ms)"
  ) +
  theme_minimal() +
  my_theme

accuracy_overall <- single_phone %>%
  summarise(
    Total_Attempts = n(),
    Successful_Trials = sum(Completed == "true", na.rm = TRUE),
    Accuracy = Successful_Trials / Total_Attempts
  )

print(accuracy_overall)



accuracy_by_level <- single_phone %>%
  filter(!is.na(Level)) %>%
  group_by(Level) %>%
  summarise(
    Total_Attempts = n(),
    Successful_Trials = sum(Completed == "true", na.rm = TRUE),
    Accuracy = Successful_Trials / Total_Attempts
  )

print(accuracy_by_level)

ggplot(accuracy_by_level, aes(x = Level, y = Accuracy)) +
  geom_line(color = "darkgreen", linewidth = 1) +
  geom_point(size = 3) +
  ylim(0,1) +
  labs(
    title = "Accuracy by Level (Single Target - Phone)",
    x = "Level",
    y = "Accuracy"
  ) +
  theme_minimal() +
  my_theme

accuracy_by_level$Accuracy <- accuracy_by_level$Accuracy * 100

```
```{r}
# Read multiple phone data
multiple_phone <- map_df(multiple_files, function(f) {
  read.csv(f)
})

str(multiple_phone)
# Clean column names
names(multiple_phone) <- make.names(names(multiple_phone))

# Convert columns to numeric
multiple_phone$SuccessRate... <- as.numeric(multiple_phone$SuccessRate...)
multiple_phone$HitRate... <- as.numeric(multiple_phone$HitRate...)

# -------------------------------
# Reaction Time stats (completed trials only)
# -------------------------------

multi_participant_stats <- multiple_phone %>%
  filter(Completed == "true", InitialResponseTime.ms. > 0, Level %in% 1:10) %>%
  group_by(PlayerID) %>%
  summarise(
    Mean_RT = mean(InitialResponseTime.ms., na.rm = TRUE),
    Mean_InterTarget = mean(AvgInterTargetTime.ms., na.rm = TRUE)
  )

multi_rt_stats <- multiple_phone %>%
  filter(Completed == "true", InitialResponseTime.ms. > 0 , Level %in% 1:10) %>%
  summarise(
    Mean_RT = mean(InitialResponseTime.ms., na.rm = TRUE),
    SD_RT = sd(InitialResponseTime.ms., na.rm = TRUE),

    Mean_Avg_RT = mean(AvgInterTargetTime.ms., na.rm = TRUE),
    SD_Avg_RT = sd(AvgInterTargetTime.ms., na.rm = TRUE)
  )

print(multi_rt_stats)

# -------------------------------
# Accuracy stats (all trials)
# -------------------------------

multi_accuracy_stats <- multiple_phone %>%
  filter(Level %in% 1:10) %>%
  summarise(
    Mean_SuccessRate = mean(SuccessRate..., na.rm = TRUE),
    SD_SuccessRate = sd(SuccessRate..., na.rm = TRUE),

    Mean_HitRate = mean(HitRate..., na.rm = TRUE),
    SD_HitRate = sd(HitRate..., na.rm = TRUE),

    Mean_FalseAlarms = mean(FalseAlarms, na.rm = TRUE),
    SD_FalseAlarms = sd(FalseAlarms, na.rm = TRUE)
  )

print(multi_accuracy_stats)

# -------------------------------
# Level-wise RT analysis
# -------------------------------

multi_level_stats <- multiple_phone %>%
  filter(Completed == "true" , Level %in% 1:10) %>%
  group_by(Level) %>%
  summarise(
    Mean_RT = mean(InitialResponseTime.ms., na.rm = TRUE),
    Mean_Avg_RT = mean(AvgInterTargetTime.ms., na.rm = TRUE),
    Mean_SuccessRate = mean(SuccessRate..., na.rm = TRUE)
  )

print(multi_level_stats)

avg_inter_target <- multiple_phone %>%
  filter(Completed == "true", AvgInterTargetTime.ms. > 0) %>%
  summarise(
    Mean_AvgInterTarget = mean(AvgInterTargetTime.ms., na.rm = TRUE),
    SD_AvgInterTarget = sd(AvgInterTargetTime.ms., na.rm = TRUE)
  )

print(avg_inter_target)
```
```{r}

my_theme <- theme_minimal() +
  theme(
    panel.border = element_rect(color = "black", fill = NA, linewidth = 1),
    axis.line = element_line(color = "black")
  )

ggplot(
  multiple_phone %>% filter(Completed == "true", InitialResponseTime.ms. > 0, Level %in% 1:10),
  aes(x = InitialResponseTime.ms.)
) +
  geom_histogram(binwidth = 500, fill = "steelblue", color = "black") +
  labs(
    title = "Reaction Time Distribution (Multiple Targets - Phone)",
    x = "Reaction Time (ms)",
    y = "Frequency"
  ) +
  theme_minimal() +
  my_theme

ggplot(
  multiple_phone %>% filter(Completed == "true", InitialResponseTime.ms. > 0, Level %in% 1:10),
  aes(x = factor(Level), y = InitialResponseTime.ms.)
) +
  geom_boxplot(fill = "steelblue") +
  labs(
    title = "Reaction Time Across Levels (Multiple Targets - Phone)",
    x = "Level",
    y = "Reaction Time (ms)"
  ) +
  theme_minimal() + 
  my_theme

ggplot(multi_level_stats, aes(x = factor(Level), y = Mean_SuccessRate)) +
  geom_bar(stat = "identity", fill = "darkgreen") +
  labs(
    title = "Average Success Rate by Level (Multiple Targets - Phone)",
    x = "Level",
    y = "Success Rate (%)"
  ) +
  ylim(0,100) +
  theme_minimal() +
  my_theme

ggplot(multi_level_stats, aes(x = Level, y = Mean_SuccessRate)) +
  geom_line(color = "darkgreen", linewidth = 1) +
  geom_point(size = 3) +
  labs(
    title = "Success Rate Trend Across Levels (Multiple Targets - Phone)",
    x = "Level",
    y = "Success Rate (%)"
  ) +
  ylim(90,100) +
  theme_minimal() +
  my_theme

ggplot(multiple_phone, aes(x = FalseAlarms)) +
  geom_histogram(binwidth = 1, fill = "orange", color = "black") +
  labs(
    title = "Distribution of False Alarms (Multiple Targets - Phone)",
    x = "Number of False Alarms",
    y = "Frequency"
  ) +
  theme_minimal() +
  my_theme

ggplot(multi_level_stats, aes(x = Level, y = Mean_RT)) +
  geom_line(color = "red") +
  geom_point(size = 2) +
  labs(
    title = "Average Reaction Time Trend Across Levels (Multiple Targets Game)",
    x = "Level",
    y = "Mean Reaction Time (ms)"
  ) +
  theme_minimal() +
  my_theme

accuracy_overall_multi <- multiple_phone %>%
  summarise(
    Total_Attempts = n(),
    Successful_Trials = sum(Completed == "true"),
    Accuracy = Successful_Trials / Total_Attempts
  )

print(accuracy_overall_multi)

accuracy_by_level_multi <- multiple_phone %>%
  filter(Level %in% 1:10) %>%
  group_by(Level) %>%
  summarise(
    Total_Attempts = n(),
    Successful_Trials = sum(Completed == "true"),
    Accuracy = Successful_Trials / Total_Attempts
  )

print(accuracy_by_level_multi)


ggplot(accuracy_by_level_multi, aes(x = Level, y = Accuracy)) +
  geom_line(color = "darkgreen", linewidth = 1) +
  geom_point(size = 3) +
  labs(
    title = "Accuracy by Level (Multiple Targets - Phone)",
    x = "Level",
    y = "Accuracy"
  ) +
  theme_minimal() +
  my_theme

accuracy_by_level_multi$Accuracy <- accuracy_by_level_multi$Accuracy * 100

inter_target_level <- multiple_phone %>%
  filter(Completed == "true", AvgInterTargetTime.ms. > 0) %>%
  group_by(Level) %>%
  summarise(
    Mean_InterTarget = mean(AvgInterTargetTime.ms., na.rm = TRUE)
  )

ggplot(inter_target_level, aes(x = Level, y = Mean_InterTarget)) +
  geom_line(color = "purple") +
  geom_point(size = 3) +
  labs(
    title = "Average Inter-Target Time Across Levels (Game)",
    x = "Level",
    y = "Average Inter-Target Time (ms)"
  ) +
  theme_minimal() +
  my_theme
```

```{r}
single_phone$Condition <- "Single"
multiple_phone$Condition <- "Multiple"

phone_combined <- bind_rows(single_phone, multiple_phone)

my_theme <- theme_minimal() +
  theme(
    panel.border = element_rect(color = "black", fill = NA, linewidth = 1),
    axis.line = element_line(color = "black")
  )

ggplot(
  phone_combined %>% filter(Completed == "true", InitialResponseTime.ms. > 0),
  aes(x = Condition, y = InitialResponseTime.ms., fill = Condition)
) +
  geom_boxplot() +
  labs(
    title = "Reaction Time Comparison (Single vs Multiple - Phone)",
    x = "Condition",
    y = "Reaction Time (ms)"
  ) +
  theme_minimal() +
  my_theme

ggplot(
  phone_combined %>% filter(Completed == "true", InitialResponseTime.ms. > 0),
  aes(x = InitialResponseTime.ms., fill = Condition)
) +
  geom_histogram(alpha = 0.6, position = "identity", binwidth = 500) +
  labs(
    title = "Reaction Time Distribution (Single vs Multiple - Phone)",
    x = "Reaction Time (ms)",
    y = "Frequency"
  ) +
  theme_minimal() +
  my_theme

accuracy_compare <- phone_combined %>%
  group_by(Condition) %>%
  summarise(
    Accuracy = mean(Completed == "true", na.rm = TRUE)
  )

print(accuracy_compare)

ggplot(accuracy_compare, aes(x = Condition, y = Accuracy, fill = Condition)) +
  geom_bar(stat = "identity") +
  ylim(0,1) +
  labs(
    title = "Accuracy Comparison (Single vs Multiple - Phone)",
    x = "Condition",
    y = "Accuracy"
  ) +
  theme_minimal() +
  my_theme

ggplot(
  phone_combined %>% filter(Completed == "true"),
  aes(x = Condition, y = FalseAlarms, fill = Condition)
) +
  geom_boxplot() +
  labs(
    title = "False Alarm Comparison (Single vs Multiple - Phone)",
    x = "Condition",
    y = "False Alarms"
  ) +
  theme_minimal() +
  my_theme
```
```{r}
############################################################
# HYPOTHESIS TESTING
############################################################
#######  Mann–Whitney U Test

######   H0: Reaction time distribution is the same for Single and Multiple conditions.
######   H1: Reaction time differs between Single and Multiple conditions.
library(dplyr)

# ----------------------------------------------------------
# 1. Mann–Whitney U Test (Single vs Multiple Reaction Time)
# ----------------------------------------------------------
# H0: Reaction time distribution is the same for Single and Multiple
# H1: Reaction time differs between Single and Multiple

mw_test <- wilcox.test(
  InitialResponseTime.ms. ~ Condition,
  data = phone_combined %>%
    filter(Completed == "true", InitialResponseTime.ms. > 0)
)

print(mw_test)
```
#### Hypothesis Testing
###### Null Hypothesis (H₀):

- There is no difference in reaction time between the Single and Multiple target conditions.

###### Alternative Hypothesis (H₁):

- There is a difference in reaction time between the two conditions.

#### Observation
Output:
- W = 12788
- p-value < 2.2e-16

###### Interpretation:

- p < 0.05 → statistically significant

- Here the p-value is extremely small

- Therefore: Reject the null hypothesis.
- Reaction times in the Single and Multiple target conditions are significantly different.
- Single RT - 3141ms
- Multiple RT - 1772ms
- Participants took significantly longer to detect targets in the Single target condition compared to the Multiple target condition.

##### Insights
- RT variable measures time to detect the first target.
- In the multiple target condition, participants can detect any of several targets, which often leads to faster initial detection.
- In the single target condition, participants must search until the specific target is found, which can increase search time.

A Mann–Whitney U test was conducted to compare reaction times between the single-target and multiple-target phone conditions. The test revealed a statistically significant difference between the two conditions (W = 12788, p < 0.001). Reaction times were significantly higher in the single-target condition compared to the multiple-target condition, indicating that detecting a single specific target required longer visual search times.

```{r}
# Level effect for Single Target (Phone)

single_level_test <- cor.test(
  single_phone$Level,
  single_phone$InitialResponseTime.ms.,
  method = "spearman"
)

print(single_level_test)
```

##### Hypothesis
Null Hypothesis (H₀)
Game level has no effect on reaction time.

Alternative Hypothesis (H₁)
Reaction time changes significantly with level.


There is a significant positive relationship between game level and reaction time. Reject H0.
As the level increases, the reaction time also increases.
This means:
Higher levels require more visual search effort and attentional processing.

```{r}
# Level effect for Multiple Target (Phone)

multi_level_test <- cor.test(
  multiple_phone$Level,
  multiple_phone$InitialResponseTime.ms.,
  method = "spearman"
)

print(multi_level_test)

inter_target_level_test <- cor.test(
  multiple_phone$Level,
  multiple_phone$AvgInterTargetTime.ms.,
  method = "spearman"
)

print(inter_target_level_test)
```
##### Hypothesis
Hypotheses

H₀: There is no relationship between level and initial reaction time.
H₁: There is a relationship between level and initial reaction time.

Interpretation

ρ = 0.1219 → very weak positive correlation
p = 0.0896 → not statistically significant (p > 0.05)

Decision:

❌ Fail to reject the null hypothesis
Meaning: Game level does not significantly affect the time to detect the first target in the multiple-target condition.

Explanation: In a multiple-target task, participants can detect any of several targets, so the first detection time does not increase much with level.


##### Hypothesis - second for multpile case
Hypotheses

H₀: There is no relationship between level and inter-target search time.
H₁: There is a relationship between level and inter-target search time.

Interpretation

ρ = 0.6465 → strong positive correlation
p < 0.001 → highly significant

Decision:
✔ Reject the null hypothesis

Meaning: There is a strong positive relationship between level and inter-target search time.
As the level increases, the time required to locate subsequent targets increases.


Explanation:
First target → can be spotted quickly among many targets
Later targets → require more searching among distractors

So difficulty mainly affects sequential search, not the first detection.


Spearman correlation analysis was conducted to examine the effect of game level on reaction time in the multiple-target condition. The relationship between level and initial reaction time was weak and not statistically significant (ρ = 0.122, p = 0.089), indicating that the time required to detect the first target did not significantly increase with level.

However, a strong positive correlation was observed between level and average inter-target time (ρ = 0.647, p < 0.001), suggesting that participants required progressively more time to locate additional targets at higher levels. This indicates that task difficulty primarily affected the sequential search process rather than initial target detection.

```{r}
# print(single_phone$InitialResponseTime.ms.)
shapiro.test(single_phone$InitialResponseTime.ms.)

boxplot(single_phone$InitialResponseTime.ms.)

shapiro.test(multiple_phone$InitialResponseTime.ms.)

boxplot(multiple_phone$InitialResponseTime.ms.)

```

#### obs
p < 0.05 , not normal, so use non - parametric tests

```{r}
# Independent Samples t-test
# Compare reaction time between Single and Multiple conditions

ind_ttest <- t.test(
  InitialResponseTime.ms. ~ Condition,
  data = phone_combined %>%
    filter(Completed == "true", InitialResponseTime.ms. > 0),
  var.equal = FALSE   # Welch t-test (safer if variances differ)
)

print(ind_ttest)
```
### obs
An independent samples t-test was conducted to compare reaction times between the single-target and multiple-target conditions. The results showed a significant difference between the two groups (t(468.51) = −7.55, p < 0.001). Participants responded faster in the multiple-target condition (M = 1741 ms) than in the single-target condition (M = 3067 ms), suggesting that detecting any one of several targets is easier than locating a specific single target.

```{r}
base <- getwd()
path <- file.path(base, "data_brsm", "single", "lab")
files <- sort(list.files(path = path,
                         pattern = "\\.csv$",
                         full.names = TRUE))

single_lab_rt <- c()
single_lab_acc <- c()
single_lab_fr <- c()
single_levelwise_rt <- NULL

for (file in files) {
  
  df <- read.csv(file)
  entries <- df$mouse.clicked_name
  entries <- entries[!is.na(entries)]
  
  all_clicks <- c()
  for (entry in entries) {
    
    clean <- gsub("\\[|\\]|'", "", entry)
    clicks <- strsplit(clean, ",")[[1]]
    clicks <- trimws(clicks)
    
    all_clicks <- c(all_clicks, clicks)
  }
  
  total_clicks <- length(all_clicks)
  hits <- sum(all_clicks == "target")
  false_clicks <- total_clicks - hits
  
  accuracy <- hits / total_clicks
  false_alarm_rate <- false_clicks / total_clicks
  
  single_lab_acc <- c(single_lab_acc, accuracy)
  single_lab_fr  <- c(single_lab_fr, false_alarm_rate)
  response_times <- df$mouse.time
  response_times <- response_times[!is.na(response_times)]
  response_times <- gsub("\\[|\\]", "", response_times)
  response_times <- as.numeric(response_times)

  single_levelwise_rt <- rbind(single_levelwise_rt, response_times)
  single_lab_rt <- c(single_lab_rt,
                          mean(response_times, na.rm = TRUE))
}

print(mean(single_lab_rt))

path1 <- file.path(getwd(), "data_brsm", "multiple", "lab")

files <- sort(list.files(path = path1,
                         pattern = "\\.csv$",
                         full.names = TRUE))

multi_lab_rt <- c()
multi_lab_acc <- c()
multi_levelwise_rt <- NULL

for (file in files) {
  
  df <- read.csv(file, stringsAsFactors = FALSE)
  
  # ----- RT calculation -----
  
  all_values <- c()
  entries <- df$mouse.time
  entries <- entries[!is.na(entries)]
  for (entry in entries) {
    
    split_lists <- strsplit(gsub("\\]\\[", "]|||[", entry), "\\|\\|\\|")[[1]]
    
    for (lst in split_lists) {
      
      clean <- gsub("\\[|\\]", "", lst)
      
      if (nchar(clean) > 0) {
        parsed <- as.numeric(strsplit(clean, ",")[[1]])
        
        if (length(parsed) > 0) {
          s <- tail(parsed, 1)
          all_values <- c(all_values, s / length(parsed))
        }
      }
    }
  }
  multi_levelwise_rt <- rbind(multi_levelwise_rt, all_values)
  multi_lab_rt <- c(multi_lab_rt, mean(all_values))
  
  
  # ----- Accuracy calculation -----
  
  entries1 <- df$mouse.clicked_name
  entries1 <- entries1[!is.na(entries1)]
  
  round_acc <- c()
  
  for (entry in entries1) {
    
    clean <- gsub("\\[|\\]|'", "", entry)
    clicks <- strsplit(clean, ",")[[1]]
    clicks <- trimws(clicks)
    
    unique_targets <- length(unique(clicks))
    
    acc <- unique_targets / 5
    
    round_acc <- c(round_acc, acc)
  }
  
  multi_lab_acc <- c(multi_lab_acc, mean(round_acc))
}

hist(single_lab_rt,
     main = "Single Lab - Mean RT",
     probability = TRUE,
     ylim = c(0, 3),
     xlab = "Mean Reaction Time",
     col = "lightblue",
     border = "black")
lines(density(single_lab_rt),
      col = "blue",
      lwd = 2)

hist(multi_lab_rt,
     main = "Multiple Lab - Mean RT",
     ylim = c(0, 3),
     probability = TRUE,
     xlab = "Mean Reaction Time",
     col = "lightgreen",
     border = "black")
lines(density(multi_lab_rt),
      col = "darkgreen",
      lwd = 2)

lab_rt = boxplot(single_lab_rt, multi_lab_rt,
        names = c("Single Target", "Multi Target"),
        main = "Lab Reaction Time Comparison",
        ylab = "Mean Reaction Time",
        col = c("lightblue", "lightgreen"),
        border = "black")

print(sd(single_lab_rt))
print(sd(multi_lab_rt))
print(mean(multi_lab_acc))
print(sd(multi_lab_acc))
single_levelwise_rt <- colMeans(single_levelwise_rt, na.rm = TRUE)
print(single_levelwise_rt, na.rm = TRUE)
print(multi_levelwise_rt)

library(ggplot2)
ggsave("lab_RT.png", plot =lab_rt , width = 6, height = 4, units = "in", dpi = 300)
```
```{r}
# Compute mean RT per player for Single Game


single_game_rt <- c()

for (file in files_game_single) {

  df <- read.csv(file)

  rt <- df$InitialResponseTime.ms.
  rt <- rt[rt > 0]

  single_game_rt <- c(single_game_rt, mean(rt, na.rm = TRUE))
}

single_compare <- data.frame(
  Lab_RT = single_lab_rt,
  Game_RT = single_game_rt
)

library(ggplot2)

ggplot(single_compare, aes(x = Lab_RT, y = Game_RT)) +
  geom_point(size = 3, color = "blue") +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  labs(
    title = "Game RT vs Lab RT (Single Target)",
    x = "Lab Reaction Time (ms)",
    y = "Game Reaction Time (ms)"
  ) +
  theme_minimal()

multi_game_rt <- multiple_phone %>%
  filter(Completed == "true", InitialResponseTime.ms. > 0) %>%
  group_by(PlayerID) %>%
  summarise(Game_RT = mean(InitialResponseTime.ms., na.rm = TRUE))

multi_lab_df <- data.frame(
  PlayerID = unique(multiple_phone$PlayerID),
  Lab_RT = multi_lab_rt
)

multi_compare <- merge(multi_game_rt, multi_lab_df, by = "PlayerID")

ggplot(multi_compare, aes(x = Lab_RT, y = Game_RT)) +
  geom_point(color = "darkgreen", size = 3) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  labs(
    title = "Game RT vs Lab RT (Multiple Target)",
    x = "Lab Reaction Time (ms)",
    y = "Game Reaction Time (ms)"
  ) +
  theme_minimal()

cor.test(single_compare$Lab_RT,
         single_compare$Game_RT,
         method = "spearman")


```

